Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
font

The stability property is then encoded by creating a
constraint of the form:
$$
\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}

@@

In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
assuming a precision \param{I_b}{F_b} 
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\tilde G(z)$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $C(z)$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

>>>>

The stability property is then encoded by creating a
constraint of the form:
$$
\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}

@@

In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
assuming a precision \param{I_b}{F_b} 
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\tilde G(z)$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $C(z)$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.
